---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cousepkg

<!-- badges: start -->
<!-- badges: end -->

The goal of cousepkg is to make plots pretty using a custom theme and `ggtext::element_markdown()` objects

## Installation

`cousepkg` requires the install of the [IBM Plex Sans](https://github.com/IBM/plex/). If you are having problems installing the fonts see a solution [here](https://github.com/wch/extrafont/issues/32#issuecomment-907556721). 

Run code below to install system fonts

```{r eval=FALSE, include=TRUE}
install.packages(extrafont)
library(extrafont)

extrafont::font_import()

```


install development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeycouse/cousepkg")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(cousepkg)
library(extrafont)
library(tidyverse)
theme_set(theme_couse())

mtcars %>%
  ggplot(aes(x = cyl))+
  geom_bar()+
  labs(x = 'Cylinders',
       y = 'Count',
       title = 'Total Cars by Cylinders',
       subtitle = '*Eight cylinder vehicles are most common*',
       caption = '**There are many cars!**')


```
