---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cousepkg

<!-- badges: start -->
<!-- badges: end -->

The goal of cousepkg is to make plots pretty using a custom theme and `ggtext::element_markdown()` objects and provide my own RMarkdown template. 

## Installation

`cousepkg` requires the install of the [IBM Plex Sans](https://github.com/IBM/plex/). The package relies on [ragg](https://github.com/r-lib/ragg) for access to system fonts.

Run code below to install system fonts

install development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeycouse/cousepkg")

```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyverse)
library(cousepkg)
theme_set(theme_couse())

mtcars %>%
  ggplot(aes(x = cyl))+
  geom_bar()+
  labs(x = 'Cylinders',
       y = 'Count',
       title = 'Total Cars by Cylinders',
       subtitle = '*Eight cylinder vehicles are most common*',
       caption = '**There are many cars!**')


```


## Source

cousepkg is largely inspired by data visualizations from [juliasilge](https://github.com/juliasilge) and her personal R Package [silgelib](https://github.com/juliasilge/silgelib)

