---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(dev = "ragg_png")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cousepkg

<!-- badges: start -->
<!-- badges: end -->

Cousepkg is a custom ggplot2 theme and ultilizes `ggtext::element_markdown()`.

## Installation

`cousepkg` requires the install of the [IBM Plex Sans](https://github.com/IBM/plex/). The package relies on [systemfonts](https://systemfonts.r-lib.org/) for access to system fonts.

install development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeycouse/cousepkg")

```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, fig.dpi=300, fig.height = 7}
library(tidyverse)
library(cousepkg)
theme_set(theme_couse())

mtcars %>%
  ggplot(aes(x = as.factor(cyl)))+
  geom_bar(aes(fill = as.factor(cyl)))+
  labs(x = 'Cylinders',
       y = '**Count**',
       title = 'Total Cars by Cylinders',
       subtitle = '*Eight cylinder vehicles are most common*',
       caption = 'There are many cars!',
       fill = "*Cylinders*") +
  theme(legend.position = c(0.15, 0.95),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.direction = "horizontal")
  


```


## Source

cousepkg is largely inspired by data visualizations from [juliasilge](https://github.com/juliasilge) and her personal R Package [silgelib](https://github.com/juliasilge/silgelib)

